State of the Practice for Lattice Boltzmann Method Software

### 2022-03-27 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
sorted table 5

\begin{table}[ht!]
	\begin{center}
		\begin{tabular}{ p{3cm}p{3cm}p{2cm}p{2cm}p{2cm} }
			\toprule
			Name & Avg.\ LOC / Text File & LOC & Text Files & Binary Files \\
			\midrule
			LUMA & 14011 & 4399723 & 314 & 19 \\
			LatBo.jl & 1029 & 42172 & 41& 0 \\
			LB2D-Prime & 668 & 54755 & 82& 19 \\
			LB3D-Prime & 563 & 12944 & 23& 6 \\
			DL\_MESO (LBE) & 549 & 170223 & 310 & 51 \\
			LB3D & 402 & 39766 & 99 & 76 \\
			laboetie & 364 & 48403 & 133& 1 \\
			waLBerla & 331 & 873988 & 2643 & 69 \\
			MechSys & 287 & 95707 & 333 & 3 \\
			Palabos & 286 & 563841 & 1974 & 71 \\
			lbmpy & 247 & 61632 & 250 & 29 \\
			SunlightLB & 212 & 7646 & 36 & 1 \\
			Musubi & 209 & 281879 & 1347 & 1839 \\
			LIMBES & 187 & 4872 & 26 & 1 \\
			Ludwig & 170 & 162518 & 954 & 32 \\
			OpenLB & 152 & 218406 & 1438 & 7 \\
			ESPResSo & 140 & 195083 & 1390& 83 \\
			MP-LABS & 140 & 43124 & 307 & 3 \\
			pyLBM & 137 & 37234 & 272 & 108 \\
			ESPResSo++ & 118 & 165194 & 1406& 30 \\
			HemeLB & 112 & 123806 & 1102& 44 \\
			Sailfish & 110 & 69398 & 632 & 11 \\
			lettuce & 105 & 7660 & 73 & 1 \\
			TCLB & 83 & 49156 & 594 & 7 \\
			\bottomrule
		\end{tabular}
		\caption{Module Data (Sorted by Avg.\ LOC / Text File)} \label{moduledata}
	\end{center}
\end{table}

>>>>

\begin{table}[ht!]
	\begin{center}
		\begin{tabular}{ p{3cm}p{2cm}p{2cm}p{2cm}p{3cm} }
			\toprule
			Name & Binary Files & LOC & Text Files & Avg.\ LOC / Text File \\
			\midrule
			LUMA & 19 & 4399723 & 314 & 14011 \\
			LatBo.jl & 0 & 42172 & 41& 1029 \\
			LB2D-Prime & 19 & 54755 & 82& 668 \\
			LB3D-Prime & 6 & 12944 & 23& 563 \\
			DL\_MESO (LBE) & 51 & 170223 & 310 & 549 \\
			LB3D & 76 & 39766 & 99 & 402 \\
			laboetie & 1 & 48403 & 133& 364 \\
			waLBerla & 69 & 873988 & 2643 & 331 \\
			MechSys & 3 & 95707 & 333 & 287 \\
			Palabos & 71 & 563841 & 1974 & 286 \\
			lbmpy & 29 & 61632 & 250 & 247 \\
			SunlightLB & 1 & 7646 & 36 & 212 \\
			Musubi & 1839 & 281879 & 1347 & 209 \\
			LIMBES & 1 & 4872 & 26 & 187 \\
			Ludwig & 32 & 162518 & 954 & 170 \\
			OpenLB & 7 & 218406 & 1438 & 152 \\
			ESPResSo & 83 & 195083 & 1390& 140 \\
			MP-LABS & 3 & 43124 & 307 & 140 \\
			pyLBM & 108 & 37234 & 272 & 137 \\
			ESPResSo++ & 30 & 165194 & 1406& 118 \\
			HemeLB & 44 & 123806 & 1102& 112 \\
			Sailfish & 11 & 69398 & 632 & 110 \\
			lettuce & 1 & 7660 & 73 & 105 \\
			TCLB & 7 & 49156 & 594 & 83 \\
			\bottomrule
		\end{tabular}
		\caption{Module Data (Sorted by Avg.\ LOC / Text File)} \label{moduledata}
	\end{center}
\end{table}
